

\documentclass[]{plushcv}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Jubayer Ahmmod}{Shuvo}{Full Stack Developer}{\contactline{\href{https://jubayerahmmodshuvo.vercel.app/}{portfolio}}{\href{https://github.com/jubayerahmmodshuvo}{jubayerahmmod}}{\href{https://www.linkedin.com/in/jubayerahmmodshuvo/}{JubayerAhmmodShuvo}}{\href{mailto:jubayerahmmod@gmail.com}{e-mail}}{\href{tel:+8801625752618}{+8801625752618}}}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.70\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    Career Objective
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Objectives}
{Enthusiastic problem solver with a passion for tackling challenges, believing they fuel continuous self-improvement. Eager to contribute innovative solutions, thrive in dynamic teams, and pursue ongoingpersonal and professional growth.}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Root Force Marketerr}
\descript{| JavaScript Engineer }
\location{June 2022 – Nov 2023 | Pune, India}
\vspace{2mm}
\begin{tightemize}
\sectionsep
\item Led the development of stable and maintainable codebases in React, implementing innovative features and functionality for improved website capabilities.
\item Contributed impactful ideas and suggestions in team meetings, consistently delivering updates on deadlines, designs, and software enhancements.
\item Contributed impactful ideas and suggestions in team meetings, consistently delivering updates on deadlines, designs, and software enhancements.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection {\href{https://budget-service.vercel.app/home}{Budget Car Service - Web Application}} 
\descript{|  {\href{https://budget-service.vercel.app/home}{Live}} | {\href{https://github.com/JubayerAhmmodShuvo/Car_Service_Front-End}{Frontend}} | {\href{https://github.com/JubayerAhmmodShuvo/car-service-backend}{Backend}}}
\location{Technologies
:
Next.js, Express.js, MongoDB, Vercel, Ant Design, TypeScript}
\begin{tightemize}
\item Assigns distinct roles to users, admins, and super-admins for efficient system management. Admins oversee user management, while super-admins supervise both admins and users.
\item Implements JWT authentication to ensure secure user login using their email and password.
\item Admins are responsible for approving service orders and can elevate users to the admin role. Super-admins have the authority to create both admin and user accounts.
\end{tightemize}
\sectionsep

\runsubsection {\href{https://taskmanagement-six.vercel.app/home}{Task Management- Web Application}} 
\descript{|  {\href{https://taskmanagement-six.vercel.app/home}{Live}} | {\href{https://github.com/JubayerAhmmodShuvo/Task_Manager_FrontEnd}{Frontend}} | {\href{https://github.com/JubayerAhmmodShuvo/Task_Management_Backend}{Backend}}}
\location{Technologies
: Next.js, Node.js, Express.js, TypeScript,
MongoDB, Tailwind, JWT}
\begin{tightemize}
\item Users register with name, email, and password; securely stored data with hashed passwords. Redirected to loginpage for subsequent access.
\item Users register with name, email, and password; securely stored data with hashed passwords. Redirected to loginpage for subsequent access.
\item "Start" button initiates task, transitioning from pending to ongoing, disabling further operations uponcompletion. Users efficiently locate and manage tasks by searching specific names. Pages display 9 tasks; post-task addition, users navigate seamlessly with pagination options.
\end{tightemize}
\sectionsep
\runsubsection {\href{https://shoehouse-frontend.vercel.app/home}{Show House - Web Application}} 
\descript{|  {\href{https://shoehouse-frontend.vercel.app/home}{Live}} | {\href{https://github.com/JubayerAhmmodShuvo/ShowHouse_Frontend}{Frontend}} | {\href{https://github.com/JubayerAhmmodShuvo/ShowHouse_Backend}{Backend}}}
\location{Technologies
: Node.js, Express.js, TypeScript,
MongoDB, Stripe, React-Hooks,
Tailwind, JWT}
\begin{tightemize}
\item Implemented robust user data protection by securely hashing passwords with bcrypt before storage in MongoDB, instilling trust in the registration process.
\item Utilized JWT authentication to seamlessly guide users through a secure login process, directing them to the login page for subsequent interactions, ensuring safeguarded credentials.
\item Integrated with Stripe, a trusted payment system, enabling users to confidently explore, order, and transact, ensuring a smooth and secure payment experience throughout the application.

\end{tightemize}









%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.25\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Frontend}
\sectionsep 
 \textbullet{} React.js \textbullet{} Next.js \textbullet{} TypeScript \textbullet{} Redux  \textbullet{} HTML5 \textbullet{} CSS3 \textbullet{} Bootstrap 5 \textbullet{} Tailwind CSS   \textbullet{}
JavaScript (ES6) \textbullet{} Ant Design \textbullet{} DaisyUI \\
\sectionsep
\subsection{Backend}
\sectionsep
Express.js \textbullet{} Node.js \textbullet{} Firebase \textbullet{} RestAPI \textbullet{} Prisma \\ 
\sectionsep
\subsection{Database}
\sectionsep
Vercel \textbullet{} Firebase \textbullet{} Netlify \textbullet{} Heroku \\
\sectionsep
\subsection{Tools}
\sectionsep
Visual Studio Code (VS Code) \textbullet{} Chrome Dev Tools \textbullet{} GitHub \textbullet{} Stack Overflow (for community and problem-solving) \\
\sectionsep
\subsection{Soft Skills}
\sectionsep
Active Listening \textbullet{} Teamwork \textbullet{} Adaptability \textbullet{} Time Management \textbullet{} \\
Mentorship and Learning \textbullet{} Curiosity \textbullet{} Attentiveness \textbullet{} Positive Attitude \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{Daffodil International University}
\vspace{2mm}
\descript{B.Sc in Computer Science \& Engineering}
\location{2018 - 2022, Dhaka}
\location{ CGPA: 3.55 / 4.0 }

\sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    Language Certificates
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Language} 
\subsection{ }
\begin{tightemize}
\item Bangla (Native)
\item English (Fluent)
\end{tightemize}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    Certificates
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Certificates} 
% \subsection{ }
% \begin{tightemize}
% \item Complete Web Development Course with Jhankar Mahbub
% \item Next Level Web Development by Programming Hero
% \item Introduction to Cybersecurity Tools \& Cyber Attacks - Coursera
% \end{tightemize}

% \sectionsep



\end{minipage} 
\end{document}  \documentclass[]{article}

